\documentclass{moderncv}
\moderncvtheme{casual}

\usepackage{comment}
\hyphenation{cabling}

\firstname{John} 
\familyname{Bush} 
\mobile{206-979-2270} 
\email{jbush.freelance@gmail.com} 
\extrainfo{GitHub: \url{https://github.com/Dzerzhinski}}

\begin{document} 
\makecvtitle

\section{Education}

\cventry{2023--present}{Graduate Certificate in Software Design \& Development}{University of Washington}{Bothell, WA}{}{Computer science and software engineering content equivalent to core requirements of a BS degree in Computer Science.}

\cventry{2021--2022}{Certificate in Ethical Hacking}{University of Washington; Professional and Continuing Education}{Seattle, WA}{}{Eight month course on professional penetration-testing.  Included cybersecurity strategies and hands-on practice.}

\cventry{2015--2018}{BS Mathematics}{University of Washington}{Bothell, WA}{}{Coursework in pure and applied math, particularly Topology, Algebra, and Linear and Nonlinear optimization and rootfinding.}

\begin{comment}
\cventry{2012--2015}{}{North Seattle College}{Seattle, WA}{}{Courses in Mathemtics and Computer Science}
\end{comment}

\begin{comment}
\cventry{2006-2007}{}{Sungkyunkwan University}{Seoul, South Korea}{}{Korean language study}


\cventry{1998--2005}{BA English, Minor Physics}{University of Washington}{Seattle, WA}{}{Studied Creative Writing.  Additional coursework in Physics and Astronomy.}
\end{comment}

\section{Employment} 

\cventry{2013--2023}{Puzzle Engineer}{Puzzle Break}{Seattle, WA}{}{Designed and fabricated puzzles for escape rooms and collaborative puzzle games. Manufactured props with sensors and microcontrollers to open locks, reveal clues, and provide players interactive puzzles.  Integrated props with off-the-shelf show control systems.  Developed backend systems for online game offerings.}

\begin{comment}
\cventry{2018}{Grader}{University of Washington}{Bothell, WA}{}{Graded homework for Real Analysis math course.  Supervised by Prof.\@ Mann.}

\cventry{2017}{Research Intern}{University of Washington}{Bothell, WA}{}{NSF-sponsored REU research program in mosaic knot theory.  Results were presented in a poster at 2018 Joint Mathematics Meeting in San Diego.  Supervised by Prof.\@ McLoud.}
\end{comment}

\begin{comment}
\cventry{2011 -- 2014}{Warehouseman}{Atlas Supply}{Seattle, WA}{}{Worked in construction supply warehouse picking orders and shipping and receiving freight.  Prepared paperwork for shipping hazardous materials.}
\end{comment}

\section{Skills}

\cvline{Programming Languages}{C, C++, Java, C\#, Python, JavaScript}

\cvline{Scientific Computing}{MATLAB, Mathematica, SciPy, R}{}{}

\cvline{Misc}{Linux, AWS (Lambda, DynamoDB, EC2), networking, cabling and low voltage digital electronics}

\section{Academic Activities} 

\begin{comment}
\cvline{2018}{Participated in Kryptos cryptanalysis challenge.  Placed second among individual competitors.} 
\end{comment}

\cvline{2017}{Participated in NSF-sponsored research project in knot theory supervised by Prof.\@ McLoud, University of Washington.}

\cvline{2016}{Participated in Mixed Reality research supervised by Prof.\@ Abadi, University of Washington.  Implemented a UWP app for Microsoft Hololens controlling motion of a robot.}

\end{document}
